---
title: "KachemakBaySampling-Manual"
author: "Martin Renner"
date: "2023-04-06"
output: pdf_document
keywords: "NOAA, NCCOS, Kasitsna Bay Lab, Kachemak Bay, Cook Inlet"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Kachhemak Bay Ecological Sampling Protocols

NOAA's Kasitsna Bay Lab, in collaboration with the Kachemak Bay Estuarine Research Reserve, has been conducting oceanographhic and ecological long-term monitoring in Kachemak Bay since 2012. This document is based on previous versions compiled by Kim Schuster and James Schloemer. Please direct question to Martin Renner [martin.renner\@noaa.gov](mailto:martin.renner@noaa.gov){.email} or Kris Holderied [kris.holderied\@noaa.gov](mailto:kris.holderied@noaa.gov){.email}.

## Sampling preparations

## Monthly and quarterly sampling

## Sample processing

## Data QAQC, analysis, and archiving

### Setup of local environment

#### Windows

The following instructions work under Windows 11. 

Install required software. 
Estimated time:


#### macOS or gnu/linux

Most code used here is cross-platform compatible. While it is possible to run all of this on a macOS or gnu/linux platform as well, proceeding here is only recommended for advanced users. The main stumbling block is processing hex-files using seabird, Inc. software, which is only available as a windows executable. It is possible to run this software on macOS or gnu/linux platforms, either within a virtual environment, like VirtualDesktop, or using wine. The following approach has worked for me (macOS 13.3, Ventura).

If not present already, install homebrew: https://brew.sh/
Install wine, using homebrew: 
** code in terminal **
brew tap homebrew/cask-versions
brew install --cask --no-quarantine wine-staging

Configure wine setup in your user account: provide access to the relevant folders.  

Copy seabird executables. 


## old R markdown stub/examples

Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
