```{r}
#| echo: false

## align wd with html dir
setwd ("~/myDocs/amyfiles/NOAA-LCI/MonthlyUpdates")
## fetch data from notebook export and CTD processing

minT = min (c(10.5, 10.6, 9.8, 11))
maxT = max (c(13, 15, 14, 12))
sDate = as.Date (Sys.Date())
sY = format (sDate, "%Y")
sM = month.name [as.numeric (format (sDate, "%m"))]
sSlot= paste (sM, sY)

crew = c("Hans", "Dom", "Martin") |> sort()
crewT = paste0 (c (paste0 (crew [1:(length (crew)-1)], collapse = ", "),
                 paste0 (crew [length (crew)])), collapse = ", and ")
# crewT


## to-do: 
## tweak title layout : remove "author" and "affiliation"
## add date? 
## add background graphics, NCCOS logo


```

---
title: "Monthly Kachemak Bay report, `{r} sSlot`"
author: 
  - name: "Martin Renner"
    email: martin.renner@noaa.gov
    affiliation:
      - name: CSS, under contract to Kasitsna Bay Lab, NCCOS, NOAA
        address: 81 Sterling Highway
        city: Homer
        state: Alaska
        postal-code: 99603

format: html  # or pdf or word
editor: visual
# title-block-style: none
# in terminal: quarto render --to pdf
---

## Conditions

On `{r} sDate`, `{r} crewT` went out to conduct our monthly survey. Water temperatures ranged from `{r} minT` degrees C at ZZ to `{r} maxT` degrees C.

Wind and precipitation. Introductory remarks

## Physical oceanography

Current conditions, long-term anomalies:

### Temperature

Absolute values and locations.

### Salinity

Salinity anomaly and seasonality. Anomaly of depth-profile.

### Stratification, turbidity, remarks

Seasonality and anomaly of strength of stratification (AlongBay 10) Seasonality of turbidity? AlongBay 02. Inner bay: glacial plume too erratic?

## Biological conditions

### Phytoplankton

Fluorescence compared to the last 12 months

Fluorescence compared to long-term mean.

### Zooplankton

Backscatter? Species composition?

### Wildlife

Sightings of whales, seaotters, birds, zooplankton.

## Appendix

<!-- Struggling with path settings -- circumvent this issue by copying relevant file to local directory -->
```{r}
#| echo: false
  ## find files
  ## construct mark-down code (all sections of the day, monthly / quarterly)
  dest="media/CTDsections/sectionImages/"
  dir.create(dest, showWarnings=FALSE, recursive=TRUE)
  
  fl <- list.files(paste0 ("~/tmp/LCI_noaa/", dest), pattern="*.png")
  flS <- grep (substr(sort (fl, decreasing=TRUE)[1], 1,10), fl, value=TRUE)
  cS <- file.copy(from=paste0 ("~/tmp/LCI_noaa/", dest, flS),
            to=dest, overwrite=TRUE
            )
  fl <- list.files (dest, pattern="*.png")
  Tran <- substr (fl, 12, nchar (fl))
  Tran <- gsub (".png", "", Tran, fixed=TRUE)
  iStrng <- paste0 ("![", Tran, "](", dest, fl, ")")
  iStrng <- paste0 (dest, fl)
  s1 <- iStrng [1]
  s2 <- iStrng [2]
  rm (fl, flS, dest, cS)
```


<!-- absolute path   file:///d:/abs -->
<!-- relative path to file: ./   -->
<!-- relative path from project root -->
<!-- shortcut path -->


<!-- relative path and ~/[path] do not seem to work for html -->

::: {#fig-elements layout-ncol=2}
![AlongBay](./`{r} s2`)

![T9](./`{r} s1`)

Longitudinal sections of main parameters.
:::
