---
title: "Kachemak Bay Oceanographic Update"
author: "Martin Renner"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Current observations, seasonal progression

Last week, XX, YY, and ZZ conducted out monthly oceanographic samplings. Temperatures ranged from -- code-chunk R min temp -- to -- code-chunk R max temp. Other comments on observed patterns of water mass, turbidity, oxygen. 

```{r, echo=FALSE}

```

Include section plots for 9 and AlongBay (and 4)

## Current state compared to long-term average 
Comments on how this compares to long-term averages, especially for temperature, salinity, and chlorophyll. 

Include Signature plots. 





Finish off with NCCOS logo. 



Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
